\documentclass[9pt,twocolumn]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
  \fi
\usepackage[dvipsnames]{xcolor}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\date{}
\usepackage{times}
\usepackage[margin=0.5in]{geometry}

\makeatletter
\newcommand{\verbatimfont}[1]{\def\verbatim@font{#1}}%
\makeatother
\usepackage{fancyvrb}


\DefineVerbatimEnvironment%
  {MyVerbatim}{Verbatim}
  {numbers=right,numbersep=2mm,firstnumber=last,stepnumber=1,xleftmargin=12pt,xrightmargin=24pt,
   frame=lines,framerule=0.1mm,fontsize=\scriptsize,rulecolor=\color{Gray}}

  \definecolor{britishracinggreen}{rgb}{0.0, 0.26, 0.15}
  
  \definecolor{bulgarianrose}{rgb}{0.28, 0.02, 0.03}
  \definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
  \usepackage{listings}
  
  \lstset{% general command to set parameter(s)
    language=Python,
    firstnumber=last,
    xleftmargin=12pt,
    xrightmargin=24pt,
    numberblanklines=false, 
    numbers=right, stepnumber=1, numberstyle=\tiny, numbersep=10pt,
    basicstyle=\linespread{0.75}\scriptsize\ttfamily, % print whole listing small
    keywordstyle=\color{coolblack}\bfseries,
    emphstyle=\ttb\color{bulgarianrose},    % Custom highlighting style
    stringstyle=\color{britishracinggreen},
    frame=tb,         
    % underlined bold black keywords
    identifierstyle=, % nothing happens
    commentstyle=\color{white}, % white comments
    stringstyle=\ttfamily, % typewriter type for strings
    showstringspaces=false} % no special string spaces
  
\begin{document} 
\small

\verbatimfont{\ttfamily\scriptsize}

%\renewcommand{\verbatim@font}{\ttfamily\small}

\hypersetup{linkcolor=black}
\setcounter{tocdepth}{3}
\tableofcontents

\input{lib}

\section{Pandoc with citeproc-hs}\label{pandoc-with-citeproc-hs}

\begin{itemize}
\item
  \textbf{???}
\item
  \textbf{???}
\item
  {[}Reference 1{]} says blah.
\item
  {[}Reference 1{]} says blah.
\item
  {[}Reference 1{]} says blah.
\item
  {[}Reference 1{]} {[}p. 30{]}, {[}3{]} says blah.
\item
  In a note.\footnote{A citation without locators 3.}
\item
  A citation group {[}1, pp. 34--35{]}, {[}3{]}.
\item
  Another one {[}1, pp. 34--35{]}.
\item
  And another one in a note.\footnote{Some citations 1--3.}
\item
  Citation with a suffix and locator {[}1, pp. 33, 35--37{]}.
\item
  Citation with suffix only 1.
\item
  Now some modifiers.\footnote{Like a citation without author: 1, and
    now Doe with a locator {[}2, p. 44{]}.}
\item
  With some markup {[}1, p. 32{]}.
\end{itemize}

\section{References}\label{references}

\input{lib.tex}

{[}1{]}J. Doe, \emph{First book}. Cambridge: Cambridge University Press,
2005.

{[}2{]}J. Doe, ``Article,'' \emph{Journal of Generic Studies}, vol. 6,
pp. 33--34, 2006.

{[}3{]}J. Doe and J. Roe, ``Why water is wet,'' in \emph{Third book}, S.
Smith, Ed. Oxford: Oxford University Press, 2007.

\end{document}
